Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/extensions.tex
lb

\paragraph{Labeled values}
%{
%format Lb = "\textbf{Labeled}"
In traditional language-based dynamic IFC systems, a label is
associated with values.
%
Hence, a program that, for example, simply writes labeled messages to
a labeled log can operate on both public and sensitive values.
%
In its simplest form, our coarse grained system requires that the
current label of a task be at least at the level of the sensitive data
to reflect the fact that such data is in scope.

Thus, an extension that allows supports such fine-grained explicitly
labeled values is essential.
%
To this end, we extend the IFC calculus with explicitly labeled
values, much like those of LIO and
Breeze~\cite{Hritcu:2013:YIB:2497621.2498098, lio}: |tv ::= cdots
inlinesep Lb il tv|.
%
Following LIO, we say that the value |tv| is protected by label |il|,
while the label |il| itself is protected by the task's current label.
%
%
Directly, the label of such values can be inspected the task without
requiring the current label to be raised.
%
However, when a task wishes to inspect the protected value |tv|, it
must first raise it label to at least |il| to reflect that it is
incorporating data at such sensitivity level in its scope.
%
Similarly, when creating labeled values the label |il| must be above
the current label; otherwise |il| cannot be said to protect the value.
%
(Importantly, we assumes that the |Lb| constructor cannot be accessed
directly to construct or destruct such values without label checks.)
%
We omit the reduction rules for labeled values since they closely
follow those presented in~\cite{lio}.
%}

>>>>

\paragraph{Labeled values}
%{
%format Lb = "\textbf{Labeled}"
%format label = "\textbf{label}"
In traditional language-based dynamic IFC systems, a label is
associated with values.
%
Hence, a program that, for example, simply writes labeled messages to
a labeled log can operate on both public and sensitive values.
%
In its simplest form, our coarse grained system requires that the
current label of a task be at least at the level of the sensitive data
to reflect the fact that such data is in scope.

Thus, an extension that allows supports such fine-grained explicitly
labeled values is essential.
%
To this end, we extend the IFC calculus with explicitly labeled
values, much like those of LIO and
Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |tv ::= cdots
inlinesep Lb il tv|.
%
Following LIO, we say that the value |tv| is protected by label |il|,
while the label |il| itself is protected by the task's current label.
%
%
Directly, the label of such values can be inspected the task without
requiring the current label to be raised.
%
However, when a task wishes to inspect the protected value |tv|, it
must first raise it label to at least |il| to reflect that it is
incorporating data at such sensitivity level in its scope.
%
When creating labeled values the label |il| must be above
the current label; otherwise it cannot be said that protection has
been transferred from the current label to |il|.
%
(For these rules, we assume that the |Lb| constructor is not part of
the surface syntax and thus cannot be accessed directly to construct
or destruct such values without label checks.)
% 
We omit the reduction rules for labeled values since they closely
follow those presented in~\cite{lio}.
%
Here, we lastly remark that that---albeit in a straight forward
way---the TSNI proof must account for this new construct, since it
appears in the IFC calculus.
%}
